---
title: "STAT 545B Assignment B1"
output: github_document
---

```{r}
# Load the libraries
library(datateachr)
library(testthat)
```


```{r}
#' Title: split_dataset
#' @details split a dataset into training and holdout sets
#' where the training set will contain 'ntrain' of examples
#' 'ntrain' must be smaller or equal to the total size of 'data'
#' @param 'data' is a data frame or tbl for the dataset
#' 'ntrain' will be numeric, 'seed' will be the numeric
#' @return a list containing both training and holdout sets 

split_dataset <- function(data, ntrain, seed) {
  stopifnot(is.numeric(ntrain))
  stopifnot(is.numeric(seed))
  stopifnot(ntrain <= nrow(data))
  set.seed(seed) # set randomness
  itrain = sample(nrow(data), ntrain)
  train = data[itrain, ]
  holdout = data[-itrain, ]
  list(train, holdout)
}
```

I am choosing data and ntrain as the names of parameters because data stands for the data set, whereas ntrain stands for the size of the split training set. Also, 'ntrain' must be smaller or equal to the total data size. The third parameter, 'seed,' is just a number we use to set seed for the function to establish some randomness in sampling the data. 

```{r}
# Examples of usage; use head to avoid printing too many rows
head(split_dataset(cancer_sample, 300, 447)[[1]]) # good
```

```{r, error=TRUE}
# Bad usage, ntrain larger than size of data
split_dataset(cancer_sample, 3000, 123) # bad
```

```{r, error=TRUE}
# Bad usage, wrong input data type
split_dataset(cancer_sample, 'c', 142) # bad
```

I propose two valid and invalid examples in the above examples. The first good case splits cancer_sample dataset into training and holdout sets and returns the (head of) training set, where the training set has 300 samples. The first invalid example is because ntrain is larger than the total size of the dataset. The second is invalid because the second parameter is not numeric. The seed is a numeric variable (random number) to generate randomness.

```{r, error=TRUE}
# Test the function
test_that("Test size of training set in valid cases", {
  expect_equal(nrow(split_dataset(cancer_sample, 300, 447)[[1]]), 300)
})
test_that("Test size of hold-out set in valid cases", {
  expect_equal(nrow(split_dataset(cancer_sample, 300, 321)[[2]]), 
               nrow(cancer_sample) - 300)
})
test_that("Test the return types in valid cases", {
  expect_equal(class(split_dataset(cancer_sample, 300, 321)), "list")
})
```

I write three tests: the first two tests the size of training and holdout sets after splitting the data. The third test tests the return type of the function. 

