---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# splitDat

<!-- badges: start -->
<!-- badges: end -->

The goal of splitDat is to split the dataset into training and holdout sets, with the size of training set specified. This way we can use the training set to train the alogrithm and then use the holdout set to test the performance of the algorithm. 

## Installation

You can install the development version of splitDat from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2022/assignment-b1-and-b2-NingyuanXu")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(splitDat)
split_dataset(cars, 30, 447)
```

The above code shows the usage of this function, which splits the dataset 'cars' into a training set and a holdout set. The size of the training set is 30, and the size of the holdout set will be the rest. The third parameter can be a random number to generate randomness in sampling the data. Note that the size of the training set must be smaller or equal to the size of the total dataset. 
